---
title: "Collaborator Analysis"
format: html
author: Aaron Angel
---

## Exercise: Explore, Clean, and Wrangle Data

```{r}
# load libraries
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(here)
```

```{r}
# read in data
lobster_traps <- read_csv(here::here("data/Lobster_Trap_Counts_All_Years_20210519.csv"))
```

```{r}
str(lobster_traps)
```
```{r}
range(lobster_traps$DATE)
```
```{r}
unique(lobster_traps$FISHING_SEASON)

unique(lobster_traps$SITE)
```
### Convert missing values using mutate() and na_if()
```{r}
unique(lobster_traps$TRAPS)
# missing values show up as -99999

```
```{r}
# convert missing values to NA
lobster_traps <- lobster_traps %>% 
  mutate(TRAPS = na_if(TRAPS, -99999))

unique(lobster_traps$TRAPS)

```
### Subset that does NOT include observations from Naples Reef (NAPL)
```{r}
lobsters_noNAPL <- lobster_traps %>% 
  filter(SITE != "NAPL")

unique(lobsters_noNAPL$SITE)

```
### Subset with lobsters at Carpinteria Reef (CARP) AND number of commercial trap floats is greater than 20
```{r}
lobsters_CARP_20 <- lobster_traps %>% 
  filter(SITE == "CARP" & TRAPS > 20)

glimpse(lobsters_CARP_20)
```
## Exercise: Data Visualization

### Multi-panel plot of lobster commercial traps (TRAPS) grouped by year
```{r}
# using ggplot(), geom_histogram(), and facet_wrap(). Use the variable YEAR in facet_wrap(). Use the object lobster_traps
ggplot(lobster_traps, aes(x = TRAPS)) +
  geom_histogram(fill = "red") +
  facet_wrap(~YEAR)

```

### Line graph of the number of total lobster commercial traps observed (y-axis) by year (x-axis) in the study, grouped by SITE
```{r}
lobster_traps_summ <- lobster_traps %>% 
  dplyr::group_by(SITE, YEAR, .drop = T ) %>% 
  summarize(TOTAL_TRAPS = sum(TRAPS, na.rm = T))

head(lobster_traps_summ)

```

```{r}
# line plot
ggplot(data = lobster_traps_summ, aes(x = YEAR, y = TOTAL_TRAPS)) +
    geom_line(aes(color = SITE))

# line and point plot
ggplot(data = lobsters_traps_summarize, aes(x = YEAR, y = TOTAL_TRAPS)) +
    geom_point(aes(color = SITE)) +
    geom_line(aes(color = SITE))
```
### Bar graph that shows the amount of high and low fishing pressure of lobster commercial traps at each SITE from 2019-2021.
```{r}
# Note: The high and low fishing pressure metrics are completely made up and are not based on any known facts.


```


